The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-09 SI.tex
Update section about wright group and bluesky

In the main body of the window, a table represents the current state of the queue and history.
More recently enqueued items appear towards the top of the table, older items towards the bottom.
The items waiting in queue, thus, appear at the top, and the items in the history appear at the bottom.
The currently running item (if it exists) appears at the boundary between the queue and the history.
The enqueued and running items have descriptions shown in bright white, while the completed items appear with gray descriptions.
The right most column indicates the position in the queue, given as a zero-based index.
Items can be reordered by editing the value in that column.
On left, there are two columns with buttons: remove and load.
Items in the queue (but not the history) can be removed individually with the red ``REMOVE'' buttons.
All items can be loaded into the sidebar where the parameters can be modified and a similar (or identical) item enqueued.
The other information provided include the plan name, the status (enqueued, RUNNING, completed, failed, aborted, stopped or unknown) and the description field, which lists the arguments passed to the plan.
Hovering over the description shows the full JSON of the item (see Figure \ref{acq:fig:hover_text}, including an error message if applicable.
The description has a contextual menu accessed via right clicking which provides additional options as shown in Figure \ref{acq:fig:right_click}.
Most of the items in the context menu simply copy information to the clipboard: The full JSON as shown by the hover text, the item \Gls{UUID} which identifies the item in the queue, and the run \Gls{UUID} which identifies the data that is collected by the scan.

The plot tab (Figure \ref{acq:fig:plot_tab} presents a live representation of recent data collected for the current plan.
The primary window is a PyQtGraph\cite{pyqtgraph} plot showing the most recent five slices of collected data.
The current slice is the brightest cyan slice, with the previous slices shown as duller colors progressively until the last one which is gray.
At the top, the currently plotted channel name and most recent collected value are shown in large font size.
The plotting does handle array detectors, for which the top number shown is the maximum value of the most recent array collected.
At present, cameras and other higher dimensional sensors are not able to be plotted using the live plot tab.
On the right hand side, there are controls to adjust the plot.
At the top, a selector allows for choosing which channel to plot.
The second selector determines which values appear along the X-axis of the graph.
In particular, to switch between a scalar channel and an array detected channel, both selectors will need to be adjusted, as the appropriate axes differ.
Additionally, there is a selector which allows for changing the units of the X-axis.
Finally, there is a Scan Index indicator, which indicates which indexed pixel was the most recent collected.

@@

\begin{landscape}
\begin{figure}
\includegraphics[width=9in]{"figures/yaqc-cmds.png"}
\caption{The main queue window of \yaqccmds{}.}
\label{acq:fig:yaqccmds}
\end{figure}
\end{landscape}

@@

\begin{landscape}
\begin{figure}
\includegraphics[width=9in]{"figures/plot_tab.png"}
\caption{\blueskycmds with the Plot tab open.}
\label{acq:fig:grid_scan}
\end{figure}
\end{landscape}

>>>>

The Wright Group uses a purpose-build graphical program to perform data acquisition.
All of the hardware used is controlled via \yaq{}.
Data is collected using Bluesky, which runs in a background process.

The graphical program includes a queue of acquisition procedures (plans, in Bluesky terminology).
In the main body of the queue window (Figure \ref{acq:fig:queue_tab}), a table represents the current state of the queue and history.
More recently enqueued items appear towards the top of the table, older items towards the bottom.
The items waiting in queue, thus, appear at the top, and the items in the history appear at the bottom.
The currently running item (if it exists) appears at the boundary between the queue and the history.
The enqueued and running items have descriptions shown in bright white, while the completed items appear with gray descriptions.
The right most column indicates the position in the queue, given as a zero-based index.
Items can be reordered by editing the value in that column.
On left, there are two columns with buttons: remove and load.
Items in the queue (but not the history) can be removed individually with the red ``REMOVE'' buttons.
All items can be loaded into the sidebar where the parameters can be modified and a similar (or identical) item enqueued.
The other information provided include the plan name, the status (enqueued, RUNNING, completed, failed, aborted, stopped or unknown) and the description field, which lists the arguments passed to the plan.
Hovering over the description shows the full JSON of the item, including an error message if applicable.

Along the left side of the window, there is a panel that allows enqueuing new items.
Figure \ref{acq:fig:grid_scan} shows the configuration panel for the most popular acquisition procedure, \texttt{grid\_scan}.
This plan allows an arbitrary number of dimensions to be scanned against one another, selecting the hardware to be scanned and the detectors to read.

The plot tab (Figure \ref{acq:fig:plot_tab}) presents a live representation of recent data collected for the current plan.
The primary window is a PyQtGraph\cite{pyqtgraph} plot showing the most recent five slices of collected data.
The current slice is the brightest cyan slice, with the previous slices shown as duller colors progressively until the last one which is gray.
At the top, the currently plotted channel name and most recent collected value are shown in large font size.
The plotting does handle array detectors, for which the top number shown is the maximum value of the most recent array collected.
At present, cameras and other higher dimensional sensors are not able to be plotted using the live plot tab.
On the right hand side, there are controls to adjust the plot.
At the top, a selector allows for choosing which channel to plot.
The second selector determines which values appear along the X-axis of the graph.
Additionally, there is a selector which allows for changing the units of the X-axis.
Finally, there is a Scan Index indicator, which indicates which indexed pixel was the most recent collected.

@@

\begin{landscape}
\begin{figure}
\includegraphics[width=9in]{"figures/queue_tab.png"}
	\caption{The main queue window of \texttt{bluesky-cmds}.}
\label{acq:fig:queue_tab}
\end{figure}
\end{landscape}

@@

\begin{landscape}
\begin{figure}
\includegraphics[width=9in]{"figures/plot_tab.png"}
	\caption{\texttt{bluesky-cmds} with the Plot tab open.}
\label{acq:fig:plot_tab}
\end{figure}
\end{landscape}
